---
title: "Getting and Cleaning Data Final Project Codebook"
author: "William Kay"
date: "6/13/2020"
output:
  html_document:
    keep_md: yes
---



<h3> Description of Output</h3>
Description of the final_output.txt file is shown below. Variables are described in detail later in this document. 

```{r echo= -1}
data<- read.table("final_output.txt", header = TRUE)
ncol(data)
nrow(data)
summary(data)
variable.names(data)
```

<h3>DESCRIPTION OF VARIABLES</h3>

<h4>subject_ID</h4>

This variable is pulled directly from the original dataset. Each ID corresponds to a unique individual. Because a given individual will have completed multiple activities, these numbers repeat. 

Information including the class, levels, and unit of measurement is described below. 

```{r echo = -1}
data<- read.table("final_output.txt", header = TRUE)
class(data$subject_ID)
unique(data$subject_ID)
```

There is no unit of measurement. Instead, each value represents a unique individual. 


<h4> activity </h4>

These lables are sourced from the activity_labels.txt file found in the original dataset and matched with the numeric id from the X_test.txt, Y_test.txt, X_train.txt, and Y_train.txt files. Each label represents a given activity carried out by the subject when measurments were taken. 

Information including the class, levels, and unit of measurement is described below. 

```{r echo = -1}
data<- read.table("final_output.txt", header = TRUE)
class(data$activity)
unique(data$activity)
```

There is no unit of measurement. Instead, each value represents a unique activity. 

<h4> variable </h4> 

These variable names are sourced from the original dataset and each corresponds to a given gyroscopic measure associated with the smartphone for a given activity. Only the data representing a mean or standard deviation were retained. 

The naming convention and more information can be found in the [features_info.txt](./UCI HAR Dataset/features_info.txt) file. 

Information including the class, levels, and unit of measurement is described below. 

```{r echo = -1}
data<- read.table("final_output.txt", header = TRUE)
class(data$variable)
unique(data$variable)
```

There is no unit of measurement. Instead, each value represents a variable from the original dataset. 

<h4> mean </h4>

These values were computed by calculating the mean of variable values for a given subject and a given activity (that is to say, the mean of the mean and the mean of the standard deviation)

Information including the class, levels, and unit of measurement is described below. 
```{r echo = -1}
data<- read.table("final_output.txt", header = TRUE)
class(data$mean)
summary(data$mean)
```

The unit of measurement is the original unit of measurement for the given variable. 

For more information please consult the [readme](./readme.md)